---
title: "Programming Background"
author: "Richard Xiao"
date: "9/6/2021"
---

```{r setup, include=FALSE, eval=FALSE}
library(rmarkdown)
library(tibble)
rmarkdown::render("HW4 blog.Rmd", output_format = github_document(
  keep_html = FALSE
), output_dir = "C:/Users/rcxia/OneDrive/Documents/ST558githubblogrepo/RichardXiao1.github.io/_posts", output_options = list(toc = TRUE , toc_depth = 3, number_sections = TRUE, df_print = "tibble")) 
knitr::opts_chunk$set(echo = TRUE)
```

## Blog Post

I think R has a lot of similarities and differences to Python, which is the other programming language I have experience with. Both have similar syntax with each other and can load packages as well as producing output such as graphs. However, R is used mainly for statistical analysis whereas Python gives a more general approach to data science. The good things that I miss about Python is the number of support libraries I have access to such as NumPy and how Python to me is easier to grasp than R. Like any other programming language, R requires extensive amount of time and practice to understand. In my other classes, I had to search up functions and help forums to broaden and develop my understanding of R, as well as reading my notes/ watching lectures. Even today, I am still learning and developing my knowledge about R.


getwd

## R Markdown output

```{r iris, echo = TRUE}
plot(iris)
```


```{r pressure, echo=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.path = "C:/Users/rcxia/OneDrive/Documents/ST558githubblogrepo/RichardXiao1.github.io/images")
```

